---
title: "SAS + R Workshop Part 1 Activity"
author: "Hunter Glanz"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Description

In this activity you will be working with the NBA_player_of_the_week.csv dataset file, located within the "Data/" subfolder of our course materials. This dataset contains information on the player of the week from the 1984-1985 season all the way up through the 2017-2018 season.

Use this RMarkdown file or a SAS script to do the following:

1. Read the dataset in

```{r}
# Your code here
```

2. Explore the variables and their values. In particular, investigate the Height and Weight variables and their values. Is there anything wrong?

```{r}
# Your code here
```

3. Fix the Height variable. Create a variable called `heightIn` that contains the player heights in inches (2.54cm = 1in). You may create other variables or do other work along the way.

```{r}
# Your code here
```

4. Fix the Weight variable. Create a variable called `weightlb` that contains the player weights in pounds (1kg = 2.20462lbs). You may create other variables or do other work along the way.

```{r}
# Your code here
```

5. Create a new variable in your dataset called timesWon which represents the number of
times each player won player of the week (Note: this value will be repeated every time a player
appears in the dataset; i.e. Tim Duncan will have a value of 23 for each of his rows/observations).

```{r}
# Your code here
```

6. Create one more variable, called recentSeason, which represents the most recent season
a player won player of the week (Note: this value be repeated every time a player appears in the
dataset; i.e. Andre Drummond will have a value of 2018 for each of his rows/observations).

```{r}
# Your code here
```
 



